Applying Deep Learning to Acoustic Analysis in the PICO-60 Dark Matter Detector

### 2018-08-09 documentation/paper.tex
Explained basic concept of ICN

>>>>

The basic concept is to start with a relatively small amount of labeled data from 2 classes (nuclear recoils and alpha particles, in this case). They can be visualized as clusters. A neural network is trained on the clusters, and used to run predictions on unlabeled data.

Those examples that, based on the network's predictions, fall firmly into one cluster or the other, are added to that cluster, and are used for training. By repeating this process, the clusters are nucleated (expanded) to gradually include more and more of the data set.
